% !TEX TS-program = lualatexmk
% !TEX parameter =  --shell-escape

\documentclass[11pt]{article}
\input{commonheaders_vespers_people}

\begin{document}

\thispagestyle{empty}

\rubrique{The cantors intone until the first barline.}

\rubrique{The melodies are those of Corpus Christi in the Roman usage.}

\grechangestyle{initial}{\fontsize{28}{28}\selectfont}
\greannotation{8.}
\gabcsnippet{(c4) O(g) sa(gh/jvIH)lu(gf)tá(hg)ris(hih) Hó(g')sti(f)a,(g.) (;) Quæ(g) cæ(i')li(j) pan(k)dis(ji) ó(hg)sti(h)um,(j.) (:) Bel(j)la(h') pre(j)munt(g) ho(gh)stí(hg)li(f)a,(g.) (;) Da(f) ro(hg)bur,(hj) fer(ji) au(hg)xí(e')li(f)um.(g.) (::) 2. U(g)ni(gh/jvIH) tri(gf)nó(hg)que(hih) Dó(g')mi(f)no(g.) (;) Sit(g) sem(i')pi(j)tér(k)na(ji) gló(hg)ri(h)a,(j.) (:) Qui(j) vi(h')tam(j) si(g)ne(gh) tér(hg)mi(f)no(g.) (;) No(f)bis(hg) do(hj)net(ji) in(hg) pá(e')tri(f)a.(g.) (::)  A(ghg)men.(fg..) (::)}
\begin{multicols}{2}
\raggedcolumns
\begin{otherlanguage}{english}
O saving victim, opening wide\\
The gate of heaven to man below,\\
Our foes press on from every side,\\
Thine aid supply, thy strength bestow.

To thy great name be endless praise,\\
Immortal Godhead, One in Three;\\
O grant us endless length of days\\
In our true native land, with thee.
Amen.
\end{otherlanguage}
\end{multicols}

\grechangestyle{initial}{\fontsize{28}{28}\selectfont}

\greannotation{3.}
\gabcsnippet{(c4) TAn(e)tum(e') er(f)go(ed) Sa(g')cra(g)mén(hj)tum(j.) (,) Ve(jk)ne(j)ré(j')mur(i) cér(h')nu(j)i:(ivHG.) (:) Et(g) an(h')tí(j)quum(i') do(h)cu(g')mén(h)tum(g.) (,) No(h')vo(i) ce(g')dat(g) rí(e')tu(h)i:(hd..) (:) Præ(e)stet(g') fi(g)des(e') sup(g)ple(h')mén(h)tum(g.) (,) Sén(h)su(i')um(g) de(hg)fé(fe)ctu(d)i.(e.) (::) (Z-) 2. Ge(e)ni(e')tó(f)ri,(ed) Ge(g')ni(g)tó(hj)que(j.) (,) Laus(jk) et(j) ju(j')bi(i)lá(h')ti(j)o,(ivHG.) (:) Sa(g)lus,(h') ho(j)nor,(i') vir(h)tus(g') quo(h)que(g.) (,) Sit(h') et(i) be(g')ne(g)dí(e')cti(h)o:(hd..) (:) Pro(e)ce(g')dén(g)ti(e') ab(g) u(h')tró(h)que(g.) (,) Com(h)par(i') sit(g) lau(hg)dá(fe)ti(d)o.(e.) (::) A(efe)men.(de..) (::)}

\begin{multicols}{2}
\raggedcolumns
\begin{otherlanguage}{english}
Down in adoration falling,\\
Lo! the sacred Host we hail;\\
Lo! o'er ancient forms departing,\\
Newer rites of grace prevail;\\
Faith for all defects supplying,\\
Where the feeble senses fail.

To the everlasting Father,\\
And the Son who reigns on high,\\
With the Holy Ghost proceeding\\
Forth from each eternally,\\
Be salvation, honour, blessing,\\
Might, and endless majesty.
Amen.
\end{otherlanguage}
\end{multicols}

   \begin{paracol}{2}

\noindent \vv Panem de cælo præstitisti eis. \tpalleluia{}\footnote{Atque per octavam Corporis Christi. \textit{As well as throughout the octave of Corpus Christi.}}

\noindent \rr Omne dele\-ctaméntum in se habéntem. \tpalleluia{}

  Orémus.
  
  \lettrine{D}{e}us, qui nobis sub Sacraménto mirábili passiónis tuæ memóriam reliquísti:~† tríbue, quǽsumus, ita nos córporis, et sánguinis tui sacra mystéria venerári;~* ut redemptiónis tuæ fructum in nobis júgiter sentiámus. Qui vivis et regnas in sǽcula sæculórum. 

  \switchcolumn
\begin{otherlanguage}{english}
\noindent \vv Thou hast given them bread from heaven. (\textit{P.T.} alleluia.)

\noindent \rr Having all sweetness within it. (\textit{P.T.} alleluia.)

\noindent Let us pray. O God, who under a wonderful Sacrament hast left us a memorial of Thy Passion; grant us, we beseech Thee, so to reverence the sacred mysteries of Thy Body and Blood, that we may ever feel within ourselves the fruit of Thy Redemption. Who livest and reignest forever and ever. Amen.
\end{otherlanguage}\end{paracol}

\begin{multicols}{2}
\raggedcolumns
\begin{otherlanguage}{english}

Blessed be God. 

Blessed be His Holy Name. 

Blessed be Jesus Christ, true God and true Man.
 
Blessed be the Name of Jesus.

Blessed be His Most Sacred Heart.

Blessed be His Most Precious Blood.

Blessed be Jesus in the Most Holy Sacrament of the Altar.

Blessed be the Holy Spirit, the Paraclete.

Blessed be the great Mother of God, Mary most Holy.

Blessed be her Holy and Immaculate Conception.

\rubrique{The following invocation is said thrice.}

Blessed be her Glorious Assumption.

Blessed be the name of Mary, Virgin and Mother.

Blessed be Saint Joseph, her most chaste spouse.

Blessed be God in His Angels and in His Saints.

\end{otherlanguage}
\end{multicols}

\rubrique{These are sung alternating between a cantor and the whole congregation, which also sings \normaltext{Fiat, Fiat} at the end.}

\gscore[]{}{laudes_divinae_no_breaks}

\rubrique{The cantors intone until the asterisk; for greater solemnity, the organ may supply the even verses.}

\rubrique{This tone is adapted from chant used by the French royal chapel and at Notre-Dame de Paris.}

\grechangestyle{initial}{\fontsize{28}{28}\selectfont}
\greannotation{\textit{Ton roy.}}
\greannotation{6.}
\gabcsnippet{Lau(f)dá(gh)te(h) Dó(h)mi(h)num(h) o(j_)mnes(ixi) gen(h)tes:(g.) * (:) lau(g)dá(g)te(g) e(g)um(g_) o(h)mnes(ixih) pó(g)pu(f)li.(f.) (::) 
Quó(h)ni(h)am(h) con(h)fir(h)má(h)ta(h) est(h) su(h)per(h) nos(h_) mi(h)se(h)ri(h)cór(j_)di(ixi)a(i) e(h)jus:(g.) (:) et(g) vé(g)ri(g)tas(g) Dó(g)mi(g)ni(g_) ma(g)net(g) in(h) æ(ixih)tér(g_)num.(f.) (::) Gló(h)ri(h)a(h_) Pa(j_)tri,(ixi) et(i) Fí(h)li(g)o,(g.) (:) et(g) Spi(g)rí(g)tu(h)i(ixih) San(g.)cto.(f.) (::) Sic(h)ut(h) e(h)rat(h) in(h) prin(h)cí(h)pi(h)o,(h_) et(h) nunc(j_) et(ixi) sem(h)per,(g.) *(:)  et(g) in(g) sǽ(g)cu(g)la(g_) sæ(g)cu(g)lo(h)rum.(ixih) A(g.)men.(f.) (::)}

\begin{otherlanguage}{english}\noindent Ps. 116: Praise the Lord, all ye nations: praise him, all ye people. For his mercy is confirmed upon us: and the truth of the Lord remaineth forever. Glory be to the Father, and to the Son, and to the Holy Ghost. As it was in the beginning, is now, and ever shall be, world without end. Amen.\end{otherlanguage}

\end{document}