\begin{otherlanguage}{english}{\centering{Prayer Before Benediction of the Most Holy Eucharist at Holy Hour}\par}

\rubrique{The priest says this prayer.}

O most sweet Jesus, who didst come into this world to enrich all souls with the life of Thy grace, and in order to preserve and foster that life within them, dost give Thyself day by day in the most adorable Sacrament of the Eucharist, as a saving remedy to heal their infirmities and a divine food to support their weakness: we humbly beseech Thee graciously to pour forth Thy Holy Spirit upon them all; so that, filled therewith, such as are defiled with deadly stain may return to Thee and recover the life of grace which they have forfeited by sin, and such as by the gift of Thy mercy already cleave to Thee may, as to each is given, approach every day Thy heavenly Banquet with true devotion. Strengthened thus, may they find herein an antidote to daily venial faults and a nourishing of the life of grace; that so being ever more and more cleansed, they may come to enjoy everlasting happiness in Heaven. ℟. Amen.

\rubrique{Then follows the prayer for the Sovereign Pontiff:}\kern 0.05em\footnote{\raggedright{Partialis indulgentia conceditur christifideli qui,…spiritu filialis devotionis, pro Summo Pontific aliquam prece legitime adprobatam pi recitaverit \textit{(e.g. Orémus pro Pontifice)} (Enchiridion Indulgentiarum, nº 25, 1º)}}

\noindent \vv Let us pray for our Pontiff, \textit{N.}

\noindent \rr The Lord preserve him, and give him life, | and make him blessèd upon the earth, | and deliver him up not up to the will of his enemies.

\noindent \vv Our Father…

\noindent \rr Give us this day…

\noindent \vv Hail Mary…

\noindent \rr Holy Mary…

\noindent \vv  Glory be…

\noindent \rr As it was…world without end. Amen.…

\rubrique{Priest:}

Almighty, everlasting God, have mercy upon Thy servant, \textit{N.,} our Sovereign Pontiff, and direct him, according to Thy clemency, into the way of everlasting salvation; that by Thy grace he may desire those things that are pleasing to Thee, and perform them with all his strength. ℟. Amen.

\rubrique{Then follows Benediction of the Most Blessed Sacrament, as usual.}


\end{otherlanguage}