\begin{otherlanguage}{english}
\rubrique{On the Second Sunday of each month, instead of the prayer \kern0.1em \normaltext{O Blessed Virgin Mary,} the following prayer is said, all kneeling.}

\rubrique{The priest says:}

O merciful God, let the glorious intercession of Thy saints assist us; above all, the most blessèd Virgin Mary, the Immaculate Mother of Thine only-begotten Son, and Thy holy apostles, Peter and Paul, through whose patronage we humbly commend this our land. Be mindful of our fathers, Thy glorious bishop John Neumann; of Junípero and Damian, Thy priests. Remember our holy martyrs who shed their blood for Christ: Isaac, René and Jean. Remember those holy virgins and widows: Frances, Rose-Philippine, Katherine, Théodore, Marianne, Kateri, and Elizabeth Ann; and all those holy men and women who made this country illustrious by their glorious merits and virtues. Let not thy memory perish before Thee, O Lord, but let their supplication enter daily into Thy sight; and do Thou, who didst so often spare Thy sinful people for the sake of Abraham, Isaac, and Jacob, now, also moved by the prayers of our fathers, brothers, and sisters reigning with Thee, have mercy up on us, save Thy people and bless Thine inheritance; and suffer not those souls to perish which Thy Son hath redeemed with His own most Precious Blood: Who liveth and reignest with Thee, world without end. ℟. Amen.
\smallskip

Let us pray.

O most loving Lord Jesus, Who, when Thou wert hanging on the Cross, didst commend us all in the person of Thy disciple John to Thy most sweet Mother, that we might find in her our refuge, our solace and our hope; look graciously upon our beloved land, and on those who are bereaved of so powerful a patronage; that acknowledging the dignity of this Holy Virgin, they may honor and venerate her with all affection of devotion, and own her as Queen and Mother. May her sweet name be listed by little ones, and linger on the lips of the agèd and dying; and may it be invoked by the afflicted, and hymned by the joyful; that this Star of the Sea being their protection and their guide, all may come to the harbor of eternal salvation. Who liveth and reignest with Thee, world without end. ℟. Amen.\end{otherlanguage}